### 2020-07-23 theory/notes_banks_buyingfinitemajorities.tex
incorporate minimization problem to theoretical section

Banks then proceeds to show that there are monotonic bribing schedules contained within the solution for equation \ref{eqn:solution}. For any $a \in \real$ let $k(a) = \lvert C(a) \rvert$. Suppose that $a\in U^l(\mathbf{v}, W_B)$ is such that $v_i \geq v_j$ and $j \in C(a)$ but $i \notin C(a)$. Then, under $A_2$, there exists $a' \in U^l(\mathbf{v}, W_B)$ with $S(a') \leq S(a)$, $k(a') = k(a)$ and $i \in C(a')$ but $j \notin C(a')$ by simply swapping $i$ for $j$. Note that since $v_i \geq v_j$, we have that $t(a) - v_i \leq  t(a) - v_j$, i.e. $a'_i \leq a_j$. $A_2$ guarantees that $a'_i \geq 0$, in other words every $i \in C(a)$ is receiving a non-negative bribe.

@@

>>>>

Banks then proceeds to show that there are monotonic bribing schedules contained within the solution for equation \ref{eqn:solution}. For any $a \in \real$ let $k(a) = \lvert C(a) \rvert$. Suppose that $a\in U^l(\mathbf{v}, W_B)$ is such that $v_i \geq v_j$ and $j \in C(a)$ but $i \notin C(a)$. Then, under $A_2$, there exists $a' \in U^l(\mathbf{v}, W_B)$ with $S(a') \leq S(a)$, $k(a') = k(a)$ and $i \in C(a')$ but $j \notin C(a')$ by simply swapping $i$ for $j$.\footnote{Note that since $v_i \geq v_j$, we have that $t(a) - v_i \leq  t(a) - v_j$, i.e. $a'_i \leq a_j$. $A_2$ guarantees that $a'_i$ or $a_j$ are non-negative.}

@@

We can now further simplify the total expenditure $S(a)$

\begin{equation*}
    S(a) = \sum_{i \in C(a)}a_i = k(a) \cdot t(a) - \sum_{i \leq k(a)}v_i
\end{equation*}

Note that the choice of $k(a)$ and $t(a)$ fully characterize any schedule $a \in U_m^l(\mathbf{v}, W_B$. We can thus fully characterize the optimization problem of $A$ as

\begin{equation*}
    \min_{k,t} k \cdot t- \sum_{i \leq k} v_i
\end{equation*}

subject to the constraint that the induced schedule $a \in U_m^l$. Banks then reformulates this as an unconstrained problem by noting the following. First, if $a(k, t, \mathbf{v})$ is unbeatable, it must be that $k \geq (n + 1)/2$, so by $A_1$ it must be that if $a_i(k, t, \mathbf{v}) = 0$, then $v_i < 0$. Therefore, $B$ receives all non-bribed voters for free. For $a(k, t, \mathbf{v})$ to be unbeatable, then, it must be that $B$ cannot afford the remaining $(n + 1)/2 - (n - k)$
